Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-11-13 manuscript.Rmd
Fix typos

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 18th window, with an exception for window 17. A peak also appeared for the 40th--42nd windows. DET was intermitently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 46th--49th windows and was below chance for extneded period from the 56th--62nd window. DET bottomed out at zero for the 15th--23rd and 34th--39th windows. The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and negative events, RR was aboce chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows. DET showed a upward trend as the windows moved. It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows. (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).

>>>>

For social cohesion and count of positive events, we saw a downward trend in RR
as the window advances throughout the sample. Interestingly, we see largely
above-chance RR until the 18th window, with an exception for window 17. A peak also appeared for the 40th--42nd windows. DET was intermittently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above or almost
above chance from the 4th--7th and 46th--49th windows and was below chance for extended period from the 56th--62nd window. DET bottomed out at zero for the 15th--23rd and 34th--39th windows. The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and negative events, RR was above chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows. DET showed a upward trend as the windows moved. It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows. (Figure
\@ref(fig:plot-wcrqa-source-targ-all)).
